Feature Selection and Classification of \\ Spam on Social Networking Sites

### 2012-05-09 docs/paper/paper.tex
update

Social networks of any significant size witness a constant flow of spam, scams and phishing attacks. 
The nature of this unwanted activity can be quite diverse, specific to a site's target audience and 
often not trivial to detect. Marketers can spam members with unwanted advertisements, fraudsters 
lure users with advance fee frauds and other confidence tricks, while others may attempt to steal user
information by directing users to external phishing pages. In contrast to email spam, social spam 
has a more personal component, since both spammers and legitimate users (``ham" users) have accompanying 
profiles with descriptive information.

Sites with global reach see communication among its members in a number foreign languages with 
varying levels of ability. This means that much benign content shares characteristics like misspellings, 
awkward phrases, etc. that might have made certain types of common frauds and spam more easy to 
distinguish on US-based (or English-language) sites.

Recent research has begun to evaluate Email spam and techniques with which to combat it has been studied 
extensively. Like

% focus on extra impact of non-public features vs. public (bag-of-words)

>>>>

Social networks of any significant size witness a constant flow of spam, scams and phishing attacks. 
The nature of this unwanted activity, which we henceforth refer to collectively as ``spam" can be 
quite diverse, specific to a site's target audience and often not trivial to detect. Marketers 
spam members with unwanted advertisements, fraudsters lure users with advance fee frauds and 
other confidence tricks, while others may attempt to steal user information by directing users 
to external phishing pages.

Sites with global reach see communication among its members in a number foreign languages with 
varying levels of ability. This means that much benign content shares characteristics including 
misspellings, awkward phrases, etc. that might have made certain types of common frauds and spam 
more easy to distinguish on US-based (or English-language) sites. Likewise, simple regional IP-based 
filtering to target high-spam countries like Nigeria and Ghana would prevent legitimate users 
located on these networks from accessing the site.

In contrast to email spam, social spam has a more personal component, since both spammers 
and legitimate users (``ham" users) have accompanying profiles with descriptive information. This can 
lead to more drawn-out, conversational attempts by spammers to approach users, since communication 
is more immediate (in the sense that users may see that they are online at the same time, may 
visit each others' profiles, etc.). However, the additional user data inherent in SNSs also 
offers a bountiful supply of data that site operators can mine to detect spam more effectively.

Most research on social networking spam has been done at a distance, using data collected 
either through scraping or artificially attracting spammers through ``honeypot" accounts. This 
paper leverages access to private messages, metadata and account details from a popular SNS 
to study the characteristics of social spam as well as the features and classifiers that 
sites can use to detect it.
